\documentclass{amsart}

\usepackage{amsmath,amssymb,amsfonts,amscd}
\usepackage[all]{xy}
\usepackage{appendix,listings,hyperref}

\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\trace}{tr}
\DeclareMathOperator{\Tor}{Tor}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\Sym}{Sym}
\DeclareMathOperator{\Hilb}{Hilb}
\DeclareMathOperator{\ch}{ch}


\newcommand{\hilb}[1]{^{[#1]}}
\newcommand{\ie}{{\it i.e. }}
\newcommand{\eg}{{\it e.g. }}
\newcommand{\loccit}{{\it loc. cit. }}
\newcommand{\vac}{|0\rangle}
\newcommand{\odd}{{\rm{odd}}}
\newcommand{\even}{{\rm{even}}}
\newcommand{\tors}{{\rm{tors}}}

\newcommand{\p}{\mathfrak{p}}
\newcommand{\pone}{ \mathfrak{p}_{ - 1} }

\newcommand{\coloneqq}{:=}
\newcommand{\kum}[2]{K_{ #2 }( #1 )}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\C}{\mathbb{C}}
\renewcommand{\H}{\mathbb{H}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\kS}{\mathfrak{S}}

\newcommand{\km}{\mathfrak{m}}
\newcommand{\kq}{\mathfrak{q}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lra}{\longrightarrow}
\newcommand{\ra}{\rightarrow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{notation}[theorem]{Notation}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Integral cohomology of $\kum{A}{2}$}


\author{Simon Kapfer}
\address{Simon Kapfer, Laboratoire de Math\'ematiques et Applications, UMR CNRS 6086, Universit\'e de Poitiers, T\'el\'eport 2, Boulevard Marie et Pierre Curie, F-86962 Futuroscope Chasseneuil}
\email{simon.kapfer@math.univ-poitiers.fr}
%\urladdr{http://www.math.uni-augsburg.de/alg/}


\date{\today}

%\keywords{}

\begin{abstract} 
What we know already
\end{abstract}

\maketitle

\section{Preliminaries}
\begin{definition}
Let $n$ be a natural number. A partition of $n$ is a decreasing sequence $\lambda = (\lambda_1,\ldots,\lambda_k),\ \lambda_1\geq\ldots\geq\lambda_k>0$ of natural numbers such that $\sum_i \lambda_i =n$. Sometimes it is convenient to write $\lambda = (\ldots,2^{m_2},1^{m_1})$ with multiplicities in the exponent.
We define the weight $\|\lambda\| :=\sum m_i i =n$ and the length $|\lambda| := \sum_i m_i =k$. 
We also define $z_\lambda \coloneqq\prod_i i^{m_i} m_i!$. 
\end{definition}
\begin{definition} \label{SymFun}
Let $\Lambda_n := \Q[x_1,\ldots,x_n]^{S_n}$ be the graded ring of symmetric polynomials. There are canonical projections $: \Lambda_{n+1}\rightarrow\Lambda_n$ which send $x_{n+1}$ to zero. The graded projective limit
$\Lambda:=\lim\limits_{\leftarrow}\Lambda_n$ is called the ring of symmetric functions.
Let $m_\lambda$ and $p_\lambda$ denote the monomial and the power sum symmetric functions. They are defined as follows: For a monomial $x_{i_1}^{\lambda_1}x_{i_2}^{\lambda_2}\ldots x_{i_k}^{\lambda_k}$ of total degree $n$, the (ordered) sequence of exponents $(\lambda_1,\ldots,\lambda_k)$ defines a partition $\lambda$ of $n$, which is called the shape of the monomial. Then we define $m_\lambda$ being the sum of all monomials of shape $\lambda$. 
For the power sums, first define $p_n := x_1^n + x_2^n + \ldots$. 
Then $p_\lambda := p_{\lambda_1}p_{\lambda_2}\ldots p_{\lambda_k}$.
The families $(m_\lambda)_\lambda$ and $(p_\lambda)_\lambda$ form two $\Q$-bases of $\Lambda$, so they are linearly related by $p_\lambda = \sum_{\mu} \psi_{\lambda\mu}m_\mu$. It turns out that the base change matrix $(\psi_{\lambda\mu})$ has integral entries, but its inverse $(\psi_{\lambda\mu}^{-1})$ has not.
\end{definition}

\section{Cohomology of Hilbert schemes of points on a torus surface}
Let $A$ be a complex projective torus of dimension $2$. Its first cohomology $H^1(A,\Z)$ is freely generated by four elements $a_1,a_2,a_3,a_4,$ corresponding to the four different circles on the torus. The cohomology ring is isomorphic to the exterior algebra:
$$
H^*(A,\Z) = \Lambda^* H^1(A,\Z).
$$
We abbreviate for the products $a_i\cdot a_j =: a_{ij}$ and $a_i\cdot a_j\cdot a_k =: a_{ijk}$. We write $a_1\cdot a_2\cdot a_3 \cdot a_4 =:x$ for the class corresponding to a point on $A$. We choose the $a_i$ such that $\int_A x = 1$.
The bilinear form, given by $(a_{ij},a_{kl})\mapsto\int_A a_{ij}a_{kl}$ gives $H^2(A,\Z)$ the structure of a unimodular lattice, isomorphic to $U^{\oplus 3}$, three copies of the hyperbolic lattice. 

Let $A\hilb{n}$ the Hilbert scheme of $n$ points on the torus, \ie the moduli space of finite subschemes of $A$ of length $n$. Their rational cohomology can be described in terms of Nakajima's operators. First consider the direct sum
$$
\H := \bigoplus_{n=0}^{\infty} H^*(A\hilb{n},\Q)
$$
This space is bigraded by cohomological \emph{degree} and the \emph{weight}, which is given by the number of points $n$. The unit element in $H^0(A\hilb{0},\Q) \cong \Q$ is denoted by $\vac$, called the \emph{vacuum}.

There are linear operators $\p_m(\alpha)$, for each $m\in \Z,\ \alpha \in H^*(A,\Q)$, acting on $\H$ which have the following properties: They depend linearly on $\alpha$, and if $\alpha\in H^k(A,\Q)$ is homogeneous, the operator $\p_{-m}(\alpha)$ is bihomogeneous of degree $k+2(|m|-1)$ and weight $m$:
$$
\p_{-m}(\alpha) : H^l(A\hilb{n}) \rightarrow H^{l+k+2(|m|-1)}(A\hilb{n+m})
$$
They satisfy the following commutation relations for $\alpha\in H^k(A,\Q),\ \beta\in H^{k'}(A,\Q)$:
$$
\p_{m}(\alpha)\p_{m'}(\beta) - (-1)^{k\cdot k'}\p_{m'}(\beta)\p_{m}(\alpha) = -m\,\delta_{m,-m'} \int_A \alpha\cdot\beta.
$$
Every element in $\H$ can be decomposed uniquely as a linear combination of products of operators $\p_{m}(\alpha),\ m<0$, acting on the vacuum. 
We abbreviate for a partition $\lambda=(\lambda_1,\ldots ,\lambda_k)$: \begin{align}
\kq_\lambda(\alpha) & := \prod_{i=1}^k \p_{-\lambda_i}(\alpha) \\
\kq_{*\lambda}(\alpha) & := \left(\prod_{i=1}^k \p_{-\lambda_i}\right)\Big(\Delta_{(k)}(\alpha)\Big)
\end{align}
For the study of integral cohomology, first note that if $\alpha \in H^*(A,\Z)$ is an integral class, then $\p_{-m}(\alpha) $ maps integral classes to integrall classes. 
Moreover, there is the following theorem:
\begin{theorem} \cite{QinWang}
The following operators map integral classes in $\H$ to integral classes:
\begin{itemize}
\item $\frac{1}{z_\lambda}\kq_{\lambda}(1)$ 
\item $\mathfrak{m}_{\lambda}(\alpha)$ for $\alpha \in H^2(A,\Z)$ 
\end{itemize}
Here, $\mathfrak{m}_{\lambda}$ is defined as $\mathfrak{m}_{\lambda}(\alpha):=\sum_{\mu} \psi^{-1}_{\lambda\mu} \kq_{-\mu}(\alpha) $ (see Definition \ref{SymFun})
\end{theorem}
%For classes $\alpha_1,\ldots ,\alpha_r \in H^*(A)$ and partitions $\lambda_1,\ldots, \lambda_r$ we write $\alpha_1^{\lambda_1}\ldots\alpha_r^{\lambda_r}$ for the class $\p_{-\lambda_1}(\alpha_1)\ldots\p_{-\lambda_r}(\alpha_r)\vac$.

To obtain the multiplicative structure of $\H$, given by the cup-products, there is a description in \cite{LehnSorger} and \cite{LiQinWang} in terms of multiplication operators $\mathfrak{G}_n(\alpha)$ \cite[Def.~5.1]{LiQinWang}, related to chern characters. 

Next we focus on the structure of $H^2(A\hilb{n},\Z)$ for $n\geq 2$. It has rank $13$, and there is a basis consisting of:
\begin{itemize}
 \item $\frac{1}{(n-1)!}\p_{-1}(1)^{n-1}\p_{-1}(a_{ij})\vac,\ 1\leq i < j\leq 4$,
 \item $\frac{1}{(n-2)!}\p_{-1}(1)^{n-2}\p_{-1}(a_{i})\p_{-1}(a_{j})\vac,\ 1\leq i < j\leq 4$,
 \item $\frac{1}{2(n-2)!}\p_{-1}(1)^{n-2}\p_{-2}(1) \vac$. We denote this class by $\delta$.
\end{itemize}
It is clear that these classes form a basis of $H^2(A\hilb{n},\Q)$. By \cite[Thm.~4.6,Lemma~5.2]{QinWang}, they also form a basis for $H^2(A\hilb{n},\Z)$. TODO: refine this argument

The first $6$ classes give an injection $j : H^2(A,\Z)\rightarrow H^2(A\hilb{n},\Z)$. 

\section{Generalized Kummer varieties}
\begin{definition}
Let $A$ be a complex projective torus of dimension $2$ and $A\hilb{n}$, $n\geq 1$, the corresponding Hilbert scheme of points. Denote $\Sigma : A\hilb{n} \rightarrow A$ the summation morphism, a smooth submersion that factorizes via the Hilbert--Chow morphism $: A\hilb{n}\rightarrow\Sym^n(A)\rightarrow A$. Then the generalized Kummer $K^{n-1} A $ is defined as the fiber over $0$:
\begin{equation}\label{square}
\begin{CD}
K^{n-1}A @>\theta >> A\hilb{n}\\
@VVV @VV\Sigma V\\
\{0\} @> >> A
\end{CD}
\end{equation}
\end{definition}
Our first objective is to collect some information about this pullback diagram. 
Or main reference is \cite{Beauville} where it is shown, that $K^{n-1}$ is an irreducible holomorphically symplectic manifold. So $H^2(\kum{A}{n-1},\Z)$ admits an integer-valued nondegenerated quadratic form (called Beauville--Bogomolov form) $q$ which gives $H^2(\kum{A}{n-1},\Z)$ the structure of a lattice isomorphic to $U^{\oplus 3}\oplus \left< -2n \right>$, for $n\geq 3$. We have the following formula for $\alpha\in H^2(\kum{A}{n-1},\Z)$:
\begin{equation} \label{fujiki}
\int_{\kum{A}{n-1}} \alpha^{2n-2} = n\frac{(2n-2)!}{2^{n-1}(n-1)!} q(a)^{n-1}
\end{equation}


The morphism $\theta$ induces a homomorphism of graded rings
\begin{equation}
\theta^* :H^*(A\hilb{n},\Z)\longrightarrow H^*(\kum{A}{n-1},\Z).
\end{equation}

\begin{proposition}Let $n\geq 3$.
\begin{enumerate} 
 \item $\theta^*$ maps $H^1(A\hilb{n},\Z)$ to zero.
 \item $\theta^*$ is surjective on $H^2(A\hilb{n},\Z)$ with kernel $\Lambda^2H^1(A\hilb{n},\Z)$.
\end{enumerate}
\end{proposition}
\begin{proof}
The first statement is clear since $H^1(\kum{A}{n-1})$ is always zero \cite[Thm.~3]{Beauville}. Furthermore, by \cite[Sect.~7]{Beauville}, $\theta^{\ast} : H^2(A\hilb{n},\C) \rightarrow H^2(\kum{A}{n-1},\C)$ is surjective. The second Betti numbers of $A\hilb{n}$ and $\kum{A}{n-1}$ are $13$ and $7$, respectively. It is clear that $\Lambda^2H^1(A\hilb{n},\Z)$ is contained in the kernel, and since the dimension of the kernel has to be $6$, it must be all.

It remains to show that $\theta^*$  is surjective for integral coefficients, too. We do it only for $n=3$. We use a formula in \cite[p. 8]{Britze}, namely:
\begin{equation} \int_{A\hilb{3}}j(a)^6 = \frac{5}{3} \int_A a^2 \int_{\kum{A}{2}} \theta^* j(a)^4
\end{equation}
for all $a\in H^2(A)$. One computes $\int_{A\hilb{3}}j(a)^6 = 15 \left(\int_A a^2\right)^3$. Comparing this with (\ref{fujiki}), we see that the sublattice given by the image of $\theta^*\circ j$ is unimodular. Secondly, we must show that $q(\theta^*\delta) = -6$. TODO: show this!
\end{proof}


\begin{proposition}
Set $a_i^{(1)}:= \frac{1}{2}\kq_1(1)^2\kq_1(a_i)\vac$. The class of $\kum{A}{2}$ in $H^4(A\hilb{3},\Q)$ is given by
$$
%\prod_{i=1}^4 \left(\tfrac{1}{2}\pone(1)^2\pone(\alpha_i)\vac\right).
a_1^{(1)}\cdot a_2^{(1)}\cdot a_3^{(1)}\cdot a_4^{(1)}.
$$ 
Conjecture: This is true for all $n$, not only $n=3$.
\end{proposition}
\begin{proof}
We know that for all $i$ and all $\beta\in H^7(A\hilb{3})$, we have $\int_ {\kum{A}{2}}\theta^*(\alpha_i\cdot\beta) = \int_ {A\hilb{3}}\alpha_i\cdot\beta \cdot[\kum{A}{2}]= 0$ and
for a basis $(\gamma_i) $ of  $H^2(A\hilb{3})$,
$$
\int_ {A\hilb{3}}\gamma_i\cdot\gamma_j\cdot\gamma_k\cdot\gamma_l\cdot[\kum{A}{2}] =
 3\left(\left<\gamma_i,\gamma_j\right>\left<\gamma_k,\gamma_l\right>+\left<\gamma_i,\gamma_k\right>\left<\gamma_j,\gamma_l\right>+\left<\gamma_i,\gamma_l\right>\left<\gamma_j,\gamma_k\right>  \right)
$$
These equations admit a unique solution.
\end{proof}
\begin{remark}
This allows us to better understand the morphism $\theta^*$. Since the Poincar\'e pairing is nondegenerated, $[\kum{A}{n-1}]\cdot \alpha=0$ implies $\theta^* \alpha =0$.
\end{remark}

Now we focus on classes of cohomological degree 4.
\begin{proposition}
The classes $\theta^* \left(\p_{-2}(a_{ij})\pone(1)\vac\right) $ and $\theta^*\left( \p_{-2}(1)\pone(a_{ij})\vac\right) $ are linearly dependent.
\end{proposition}
\begin{proof}
We can compute the product of these two classes with $[ \kum{A}{2} ] $ in $H^*(A\hilb{3})$. The two results are linearly dependent. Is there a direct geometric proof?
\end{proof}

\begin{proposition}
$\theta^*\left(\p_{-3}(x)\vac\right) =0$ 
\end{proposition}
\begin{corollary}
$\theta^* \left(\p_{-2}(a_{ij})\pone(1)\vac\right) = \frac{1}{4}\theta^*\left( \p_{-2}(1)\pone(a_{ij})\vac\right) $
\end{corollary}
\begin{proof}
Let  $a_{ij}$ and $a_{kl}$ be complementary, \ie $a_{ij}a_{kl}=1$. Let $\ch_1(a_{kl}) = -\frac{1}{2} \p_{-2}(a_{kl})\pone(1)\vac$ be the chern character in the vertex algebra description of $H^*(A\hilb{3})$. Then:
$$
\theta^*\left(-\frac{1}{2}\ch_1(a_{kl})\cdot\p_{-2}(a_{ij})\pone(1)\vac \right) =
\theta^*\left(\p_{-3}(1)\vac + \frac{1}{2}\pone(x)^2\pone(1)\vac \right)
$$
But on the other hand, $\delta \cdot j(a) = \frac{1}{2} \p_{-2}(1)\pone(a_{ij})\vac+\p_{-2}(a_{ij})\pone(1)\vac$, and
$$
\theta^*\left(\ch_1(a_{kl})\cdot \delta \cdot j(a)\right) =
\theta^*\left(-3\p_{-3}(1)\vac  - 3\pone(x)^2\pone(1)\vac \right).
$$
\end{proof}
\begin{corollary}
$\theta^*\left( \delta \cdot j(a_{ij}) \right) = \theta^*\left( \frac{3}{4} \p_{-2}(1)\pone(a_{ij})\vac\right)$ is divisible by 3. \qed
\end{corollary}
\begin{proposition}
The classes $\theta^*\left(j(a_{ij})^2 - \frac{1}{3}j(a_{ij})\cdot \delta\right)$ are divisible by 2.
\end{proposition}
\begin{proof}
By \cite{QinWang}, the classes $\frac{1}{2} \pone(a_{ij})^2\pone(1)\vac - \frac{1}{2}\p_{-2}(a_{ij})\pone(1)\vac$ are integral in $H^4(A\hilb{n})$. But $j(a_{ij})^2= \pone(a_{ij})^2\pone(1)\vac $ and $\theta^*\left(\frac{1}{3}j(a_{ij})\cdot\delta\right) =\theta^*\left(\p_{-2}(a_{ij})\pone(1)\vac\right)$.
\end{proof}
\begin{proposition}
The class $\delta^2$ is divisible by 2.
\end{proposition}
\begin{proof}
By \cite[Prop.~4.1]{HassettTschinkel}, $\Sym^2H^2 \oplus \left(\Sym^2H^2\right)^\perp = H^4$. 
We want to show that $\delta^2\cdot \Sym^2H^2 = 2\Z$. We know a $\Q$--basis of $\Sym^2H^2$ with at most one class divisible by 2, given by $j(a_{ij})j(a_{kl})$, $\delta^2$ and the above proposition. By computation, $\int \delta^4$ is divisible by 4 and $\int \delta^2 j(a_{ij})j(a_{kl})$ and $\int \delta^3 j(a_{ij})$ are all divisible by 2.
So $\delta^2\cdot H^4 = 2\Z$ and therefore $\delta^2$ is divisible by $2$, since $ H^4 $ is unimodular.
\end{proof}

\begin{proposition}
The class $\theta^*\left(\delta^2 - j(a_1)\cdot j(a_2)- j(a_3)\cdot j(a_4)- j(a_5)\cdot j(a_6)\right)$ is divisible by 3.
\end{proposition}
\begin{proof}
It is equal to $\theta^*\left(\p_{-3}(1)\vac +\frac{3}{2}\pone(x)\pone(1)^2\vac \right)$.
\end{proof}

Next we look at the Chern classes of the tangent sheaves. Since the morphism $\Sigma$ from the defining pullback diagram (\ref{square}) is a submersion, the normal bundle of $\kum{A}{n-1}$ in $A\hilb{n}$ is trivial. Hence $c(\kum{A}{2}) = \theta^* c(A\hilb{3})$. Looking in \cite[Sect.~8]{Generating}, we find a general formula for Chern classes of Hilbert schemes of points on surfaces. So we deduce
\begin{align*}
c_2(A\hilb{3}) &= \left(\tfrac{3}{2} \mathfrak{q}_{*(1,1)}(1) \mathfrak{q}_1(1) -\tfrac{1}{3} \mathfrak{q}_3\right)\vac \\
 &= 10(1\hilb{\bullet}_{(4)})  -2(1\hilb{\bullet}_{(2)})^2 \\
c_4(A\hilb{3}) &= \tfrac{4}{3} \mathfrak{q}_{*(1,1,1)}( 1)\vac = 4 (1\hilb{\bullet}_{(4)})^2. 
\end{align*}



\bibliographystyle{amsplain}
\bibliography{Kummer2.tex}
\end{document}
