\bibliographystyle{amsplain}
\begin{thebibliography}{10}

\bibitem{Beauville}
Arnaud Beauville, \emph{Vari\'et\'es k\"ahleriennes dont la premi\`ere classe de Chern est nulle}, 
  J. Differential geometry~\textbf{18} (1983), 755--782.

\bibitem{Boissiere}
Samuel Boissi\`ere, \emph{Chern classes of the tangent bundle on the Hilbert scheme of points
  on the affine plane}, J.~Algebraic Geom.~\textbf{14} (2005), 761--787.

\bibitem{Generating}
Samuel Boissi\`ere and Marc Nieper-Wi{\ss}kirchen, \emph{Generating series in the cohomology 
  of Hilbert schemes of points on surfaces}, LMS J.~of Computation and Math.~\textbf{10} (2007), 254--270.

\bibitem{BNS2}
Samuel Boissière, Marc Nieper-Wi\ss kirchen and Alessandra Sarti, 
\emph{Higher dimensional Enriques varieties and automorphisms of generalized Kummer varieties},
Journal de Mathématiques Pures et Appliquées~\textbf{95} (2011), no. 5, 553--563.

\bibitem{BNS}
Samuel Boissière, Marc Nieper-Wi\ss kirchen and Alessandra Sarti, \emph{Smith theory and 
  Irreducible Holomorphic Symplectic Manifolds}, J.~of Topology~\textbf{6} (2013), no.~2, 361--390.

\bibitem{Borcea}
Ciprian~Borcea,
\emph{Diffeomorphisms of a K3 surface},
Math. Ann.~\textbf{275} (1986), no.~1, 1--4.  
  
\bibitem{Bredon}
Glen E.~Bredon,
\newblock \emph{Intoduction to compact transformation groups},
Pure and Applied Mathematics, Vol. 46,
Academic Press, New York
(1972).

\bibitem{Britze} 
Michael Britze, \emph{On the cohomology of generalized Kummer varieties}, PhD thesis, Universit\"at zu K\"oln (2003). 

\bibitem{Chihara}
Theodore~S.~Chihara, \emph{An introduction to orthogonal polynomials},
  Mathematics and its Applications 13, Gordon and Breach Science Publishers (1978).

\bibitem{Dai}
Feng~Dai and Yuan~Xu, \emph{Spherical Harmonics} (2013), \href{http://arxiv.org/abs/1304.2585}{arXiv:1304.2585}.

\bibitem{Denes}
J\'ozsef~D\'enes, \emph{The representation of a permutation as the product of a minimal number of
  transpositions, and its connection with the theory of graphs}, Publ. Math. Institute Hung. Acad. Sci.
 ~\textbf{4} (1959), 63--71.

\bibitem{Dolgachev}
Igor V.~Dolgachev, \emph{Classical Algebraic Geometry}, 
  Cambridge University Press (2012).

\bibitem{Dunkl}
Charles~F.~Dunkl and Yuan~Xu, \emph{Orthogonal Polynomials of Several Variables},
  Encyclopedia of Mathematics and its Applications, Vol.~81, Cambridge University Press (2001).

\bibitem{EGL}
Geir Ellingsrud, Lothar G\"ottsche and Manfred Lehn, \emph{On the Cobordism Class of the Hilbert 
  Scheme of a Surface}, J.~of Algebraic Geom.~\textbf{10} (2001), 81--100. 

\bibitem{Farb}
Benson~Farb and Dan~Margalit \emph{A primer on mapping class groups}, Princeton University Press (2012).

\bibitem{Fogarty}
John Fogarty, \emph{Algebraic Families on an Algebraic Surface},
  Am.~J.~Math.~\textbf{10} (1968), 511--521.

\bibitem{Folland}
Gerald~B.~Folland, \emph{How to Integrate a Polynomial over a Sphere}, The American
  Mathematical Monthly, Vol.~108, no.~5, (2001).

\bibitem{FujikiK}
Akira Fujiki
\emph{A theorem on bimeromorphic maps of Kähler manifolds and its applications},
Publ. Res. Inst. Math. Sci., 
\textbf{17} (1981), no. 2, 735--754.

\bibitem{Fujiki}
Akira Fujiki, \emph{Finite automorphism groups of complex tori of dimension two}, Publ. RIMS,
  Kyoto Univ.~\textbf{24} (1988), 1--97.

\bibitem{Fujiki2}
Akira Fujiki,
\emph{On Primitively Symplectic Compact K\"ahler V-manifolds of Dimension Four},
Classification of algebraic and analytic manifolds, Progr.~Math.~\textbf{39}
(1982), 71--250.

\bibitem{Fulton}
William~Fulton,
\emph{Intersection theory},
Second edition, Springer (1998).

\bibitem{Ghys}
Etienne Ghys and Alberto Verjovsky, \emph{Locally free holomorphic actions of the complex affine group},
  Geometric Study of Foliations, World Scientific (1994), 201--217.

\bibitem{Gottsche}
Lothar~G\"ottsche, \emph{Hilbert Schemes of Zero-Dimensional Subschemes of Smooth Varieties},
  Lecture Notes in Mathematics 1572, Springer (1994).

\bibitem{Hassett}
Brendan~Hassett and Yuri~Tschinkel, \emph{ Hodge theory and Lagrangian planes on 
  generalized Kummer fourfolds}, Moscow Math.~Journal~\textbf{13} (2013) no. 1, 33--56. 

\bibitem{Huybrechts}
Mark~Gross, Daniel~Huybrechts and Dominic~Joyce, \emph{Calabi-Yau Manifolds and Related Geometries},
  Universitext, Springer (2003).
  
\bibitem{Kapfer2}
Simon Kapfer, \emph{Computing cup products in integral cohomology of Hilbert schemes of points on K3 surfaces},
  LMS J.~of Computation and Math.~\textbf{19} (1), 78--97, DOI: \href{http://dx.doi.org/10.1112/S1461157016000012}{10.1112/S1461157016000012}.

\bibitem{Kapfer}
Simon~Kapfer, \emph{Symmetric Powers of Symmetric Bilinear Forms, Homogeneous Orthogonal Polynomials 
  on the Sphere and an Application to Compact Hyperk\"ahler Manifolds}, Commun.~Contemp.~Math.~(2016), DOI: \href{http://dx.doi.org/10.1142/S0219199716500073}{10.1142/S0219199716500073}.

\bibitem{Tim}
Tim~Kirschner, \emph{Irreducible symplectic complex spaces}, PhD thesis, Univ.~Bayreuth (2012), 
\href{http://arxiv.org/abs/1210.4197}{arXiv:1210.4197}.

\bibitem{Lascoux}
Alain Lascoux, \emph{Symmetric functions}, Notes of the course given at Nankai University (2001),\\
  \href{http://www.mat.univie.ac.at/~slc/wpapers/s68vortrag/ALCoursSf2.pdf}{http://www.mat.univie.ac.at/\~{}slc/wpapers/s68vortrag/ALCoursSf2.pdf}.

\bibitem{LehnSorger}
Manfred Lehn and Christoph Sorger, \emph{The cup product of Hilbert schemes for {$K3$}
  surfaces}, Invent. Math.~\textbf{152}, no.~2 (2003), 305--329.

\bibitem{LiQinWang2}
Wei-Ping Li, Zhenbo~Qin and Weiqiang~Wang, \emph{Hilbert schemes and W algebras}, Int.~Math.~res.~Not.~\textbf{27} (2002),
 1427--1456.

\bibitem{LiQinWang}
Wei-Ping Li, Zhenbo~Qin and Weiqiang~Wang, \emph{Vertex algebras and the cohomology ring structure of 
  Hilbert schemes of points on surfaces}, Math.~Ann.~\textbf{324}, no.~1 (2002), 105--133.
  
\bibitem{Markman}
Eyal~Markman, \emph{Integral generators for the cohomology ring of moduli spaces of
  sheaves over Poisson surfaces}, Adv. Math.~\textbf{208} (2007), no.~2,
  622--646.

\bibitem{Markman2}
Eyal~Markman, \emph{Integral constraints on the monodromy group of the
  hyperk\"ahler resolution of a symmetric product of a {$K3$} surface},
  Internat. J. Math.~\textbf{21} (2010), no.~2, 169--223.

\bibitem{Markmanou}
Eyal~Markman and Sukhendu~Mehrtra,
\emph{Hilbert schemes of K3 surfaces are dense in moduli},
\href{http://arxiv.org/abs/1201.0031v1}{arXiv:1201.0031v1}.

\bibitem{Mat}
Daisuke~Matsushita,
\emph{On base manifolds of Lagrangian fibrations},
Science China Mathematics (2014), 531--542.

\bibitem{Lol2}
Gr\'egoire~Menet,
\emph{Beauville--Bogomolov lattice for a singular symplectic variety of dimension 4},
Journal of pure and applied algebra (2014), 1455--1495.

\bibitem{Lol}
Gr\'egoire~Menet,
\emph{Cohomologie enti\`ere et fibration lagrangiennes sur certaines vari\'et\'es holomorphiquement symplectiques singuli\`eres},
PhD thesis of Lille 1 University, (2014).

\bibitem{McGarr}
Se\'an McGarraghy, \emph{Symmetric Powers of Symmetric Bilinear Forms}, 
  Algebra Colloquium~\textbf{12} (2005), no.~1, 41--57.

\bibitem{Milne}
James~S.~Milne, \emph{Abelian Varieties (v2.00)}, Available at \href{http://www.jmilne.org/math/}{www.jmilne.org/math/} (2008).

\bibitem{Milnor}
John~Milnor and Dale~Husem\"oller, \emph{Symmetric bilinear forms}, Ergebnisse der Mathematik
  und ihrer Grenzgebiete 73, Springer (1973).

\bibitem{Mongardi}
Giovanni~Mongardi,
\emph{Symplectic involutions on deformations of $K3^{[2]}$},
Cent. Eur. J. Math. 
\textbf{10} (2012), no.~4, 1472--1485.

\bibitem{MongWanTari}
Giovanni~Mongardi, Kévin Tari and Malte Wandel,
\emph{Automorphisms of generalised Kummer fourfolds},
\href{http://arxiv.org/abs/1512.00225v2}{arXiv:1512.00225v2}. 

\bibitem{MongWanTari0}
Giovanni~Mongardi, Kévin Tari and Malte Wandel,
\emph{Prime order automorphisms of abelian surfaces: a lattice-theoretic point of view},
\href{http://arxiv.org/abs/1506.05679v1}{arXiv:1506.05679v1}. 

\bibitem{Mumford}
David~Mumford, \emph{Abelian varieties}, Tata Institute of Fundamental Research Studies in Mathematics, 
  No.~5 (1970).

\bibitem{Nakajima}
Hiraku~Nakajima, \emph{Heisenberg algebra and Hilbert schemes of points on
  projective surfaces}, Ann. of Math. (2)~\textbf{145} (1997), no.~2, 379--388.

\bibitem{Nanikawa}
Yoshinori~Namikawa,
\emph{Extension of 2-forms and symplectic varieties},
J. Reine Angew. Math. 
\textbf{539} (2001), 123--147.

\bibitem{Twisted}
Marc Nieper-Wißkirchen,
\emph{Twisted Cohomology of the 
	Hilbert Schemes of Points on Surfaces}
	Documenta Math.~\textbf{14} (2009) 749--770.

\bibitem{Lattice}
Viacheslav V.~Nikulin,
\emph{Integral symmetric bilinear forms and some of their applications},
Math. USSR Izv.
\textbf{14} (1980), 103--167.

\bibitem{OGrady}
Kieran~G.~O'Grady, \emph{Compact Hyperk\"ahler manifolds: general theory}, lecture notes (2014),
  \href{http://www.mimuw.edu.pl/~gael/Document/hk-theory.pdf}{http://www.mimuw.edu.pl/~gael/Document/hk-theory.pdf}.

\bibitem{Oguiso}
Keiji~Oguiso,
\emph{No cohomologically trivial non-trivial automorphism of generalized Kummer manifolds},
\href{http://arxiv.org/abs/1208.3750}{arXiv:1208.3750}.

\bibitem{haskell98}
Simon Peyton Jones and others,
  \emph{The {Haskell} 98 Language and Libraries: The Revised Report},
  J. of Functional Programming~\textbf{13} (2003), no.~1, 0--255.

\bibitem{QinWang}
Zhenbo~Qin and Weiqiang~Wang, \emph{Integral operators and integral cohomology classes of
  {H}ilbert schemes}, Math. Ann.~\textbf{331} (2005), no.~3, 669--692.

\bibitem{Rapagnetta}
Antonio~Rapagnetta,
\emph{On the Beauville form of the known irreducible symplectic varieties},
Math. Ann.
\textbf{321} (2008), 77-95.

\bibitem{Scattone}
Francesco~Scattone, \emph{On the compactification of moduli spaces for algebraic K3 surfaces},
  Memoirs of the American Mathematical Society (1987), Volume 70, Number 374.

\bibitem{Shioda}
Tetsuji~Shioda, \emph{The period map of abelian surfaces}, J. Fac. S. Univ. Tokyo~\textbf{25} (1978), 47--59.

\bibitem{Spanier}
Edwin~Spanier, 
\emph{The homology of Kummer manifolds},
Proc. Amer. Math. Soc.~\textbf{7} (1956), 155--160.

\bibitem{Tari}
K\'evin~Tari, 
\emph{Automorphismes des vari\'et\'es de Kummer g\'en\'eralis\'ees},
PhD thesis, Université de Poitiers (2015).

\bibitem{Totaro}
Burt~Totaro, \emph{The integral cohomology of the Hilbert scheme of two points}, 
\href{http://arxiv.org/abs/1506.00968}{arXiv:1506.00968}.

\bibitem{Verbitsky}
Misha~Verbitsky, \emph{Cohomology of compact hyperk\"ahler manifolds and its
  applications}, Geom. Funct. Anal.~\textbf{6} (1996), no.~4, 601--611.

\bibitem{Voisin}
Claire~Voisin, \emph{Hodge Theory and Complex Algebraic Geometry, I},
  Cambridge studies in advanced mathematics 76, Cambridge University Press (2002).

\end{thebibliography}
