
\chapter{Lattices}\label{latticeSubsection}
Let us first recall some elementary facts about lattices that will be needed throughout the text.
A reference for this section is Chapter 8.2.1 of \cite{Dolgachev}. 
\begin{definition}
By a \emph{lattice} $L$ we mean a free $\Z$--module of finite rank, equipped with a non-degenerate, integer-valued symmetric bilinear form, denoted by $B$ or $\left<\ ,\;\right>$. 
By a homomorphism or \emph{embedding} $L\subset M$ of lattices we mean a map $:L\rightarrow M$ that preserves the bilinear forms on $L$ and $M$ respectively. It is automatically injective. We always have the injection of a lattice $L$ into its dual space $L^*\coloneqq \Hom(L,\Z)$, given by $x \mapsto \left<x,\ \right>$. A lattice is called \emph{unimodular}, if this injection is an isomorphism, \ie if it is surjective. By tensoring with $\Q$, we can interpret $L$ as well as $L^*$ as a discrete subset of the $\Q$--vector space $L\otimes \Q$. Note that this gives a kind of lattice structure to $L^*$, too, but the symmetric bilinear form on $L^*$ may now take rational coefficients.


If $L\subset M$ is an embedding of lattices of the same rank, then the \emph{index} $|M\DP L|$ of $L$ in $M$ is defined as the order of the finite group $M/L$.
There is a chain of embeddings $L\subset M \subset M^* \subset L^*$ with $|L^*\DP M^*| =|M\DP L| $.

The quotient $L^*/L$ is called the \emph{discriminant group} and denoted $A_L$. The index of $L$ in $L^*$ is called $\discr L$, the \emph{discriminant} of $L$.
Choosing a basis $(x_i)_i$ of $L$, we may express $\discr L$ as the absolute value of the determinant of the so-called \emph{Gram matrix} $G$ of $L$, which is defined by $G_{ij}\coloneqq \left<x_i,x_j\right>$. $L$ is unimodular, if and only if $\det G =\pm 1$.

The lattice $L$ is called \emph{odd}, if there exists a $v\in L$, such that $\left<v,v\right>$ is odd, otherwise it is called \emph{even}. 
If the map $v \mapsto \left<v,v\right>$ takes both negative and positive values on $L$, the lattice is called \emph{indefinite}. 
\end{definition}
\begin{example}
Up to isomorphism there is a unique even unimodular lattice of rank two. It is called the \emph{hyperbolic lattice} $U$. Its Gram matrix is given by 
$\left(\begin{smallmatrix} 0&1\\ 1&0 \end{smallmatrix}\right)$.
\end{example}
\begin{proposition} \label{squareDiscr}Let $M$ be a lattice. Let $L\subset M$ be a sublattice of the same rank. Then $|M\DP L|$ equals $\sqrt{\frac{\discr L}{\discr M}}$.
\end{proposition}
\begin{proof}
%Since $M$ is unimodular, $|L^*\DP M|=|L^*\DP M^*| =|M\DP L| $ and therefore $|L^*\DP L| = |L^*\DP M||M\DP L|  = |M\DP L|^2$.
We have $|L^*\DP L|=|L^*\DP M^*||M^*\DP M||M\DP L|$. Hence:
$\frac{|L^*\DP L|}{|M^*\DP M|}=|L^*\DP M^*||M\DP L|=|M\DP L|^2.$
\end{proof}
An embedding $L\subset M$ is called \emph{primitive}, if the quotient $M/L$ is free. We denote by $L^\perp$ the orthogonal complement of $L$ within $M$. Since an orthogonal complement is always primitive, the double orthogonal complement $ L^{\perp\perp}$ is a primitively embedded overlattice of $L$. It is clear that $\discr( L^{\perp\perp})$ divides $\discr L$. 
\begin{proposition}\label{TorsionQuotient} Let $L\subset M$ be an embedding of lattices. Then the order of the torsion part of $M/L$ 
divides $\discr L$.
\end{proposition}
\begin{proof}
The torsion part is the index of $M/( L^{\perp\perp})$ in $M/L$. But this is equal to $|L^{\perp\perp}\DP L| = |L^* \DP (L^{\perp\perp})^*|$ and clearly divides $|L^*\DP L|$.
\end{proof}
\begin{proposition}\label{discrOrthPrim}
Let $M$ be unimodular. Let $L\subset M$ be a primitive embedding. Then $\discr L = \discr L^\perp$.
\end{proposition}
\begin{proof}
Consider the orthogonal projection $ : M\otimes\Q \rightarrow L\otimes \Q$. Its restriction to $M$ has kernel equal to $L^\perp$ and image in $L^*$. Hence we have an embedding of lattices $M/L^\perp \subset L^*$. Quotienting by $L$, we get an injective map $: M/(L\oplus L^\perp) \rightarrow L^*/L$. 
Now by Proposition~\ref{squareDiscr}, $\sqrt{\discr(L) \discr (L^\perp)} =|M \DP (L\oplus L^\perp)| \leq |L^*\DP L| = \discr L$. So we get $\discr L^\perp \leq \discr L$. Exchanging the roles of $L=L^{\perp\perp}$ and $L^\perp$ gives the inequality in the opposite direction.
\end{proof}
\begin{corollary}\label{latticeCor}
Let $L\subset M$ be an embedding of lattices with unimodular $M$. Let $n$ be the order of the torsion part of $M/L$. Then $\discr L^\perp =\discr L^{\perp\perp} = \frac{1}{n^2}\discr L$.
\end{corollary}

\begin{example}
Given a free $\Z$-module $L$ with the structure of a commutative ring and a linear form $I:V\rightarrow \Z$, the setting $\left<v,w\right>=I(vw)$ defines a bilinear form giving $L$ the structure of a lattice if it is non-degenerate. This is the case in topology:
For a compact complex manifold $X$ of dimension $d$ Poincar\'e duality induces a non-degenerate bilinear form on $H^d(X,\Z)$: 
$$
\left<\alpha,\beta\right> = \int_X\alpha\beta.
$$ 
This unimodular lattice will be referred to as the \emph{Poincar\'e lattice}.
\end{example}